%%This is a very basic article template.  %%There is just one section and two
%%subsections.  
\documentclass[sigconf]{acmart}
\citestyle{acmauthoryear}

%\usepackage{cite} 
\usepackage{natbib}
\usepackage{tabularx}
\usepackage[autostyle]{csquotes} 
\usepackage{url} 
\usepackage{todonotes}
\usepackage{float}
\usepackage{array}
\usepackage{tabu}

% Conference info
\acmConference[Short name]{Long name}{November 2017}{Denver, Colorado USA}
\acmYear{2017}
\copyrightyear{2017}


\begin{document}

\title{A Comprehensive Ontology for Scientific Workflows}

\author{Jay Jay Billings}
\orcid{orcid.org/0000-0001-8811-2688}
\affiliation{
\institution{Oak Ridge National Laboratory}
\institution{The Bredesen Center for Interdisciplinary Research and Graduate Education, The University of Tennessee - Knoxville}
\streetaddress{PO Box 2008 MS 6173}
\city{Oak Ridge}
\state{TN}
\country{USA}
\postcode{37831}}
\email{billingsjj@ornl.gov \\ Twitter: @jayjaybillings} 

%\author{Shantenu Jha}
%\affiliation{
%\institution{Computational Science Initiative, Brookhaven National Laboratory and Rutgers University}
%\city{Upton}
%\state{NY}
%\country{USA}
%\postcode{11973}}
%\email{shantenu.jha@rutgers.edu}

\begin{abstract}


\end{abstract}

\maketitle

\underline{Notice of Copyright:} This manuscript has been authored by UT-
Battelle, LLC under Contract No. DEAC05-00OR22725 with the U.S. Department of
Energy. The United States Government retains and the publisher, by accepting
the article for publication, acknowledges that the United States Government
retains a nonexclusive, paid-up, irrevocable, world-wide license to publish or
reproduce the published form of this manuscript, or allow others to do so, for
United States Government purposes. The Department of Energy will provide
public access to these results of federally sponsored research in accordance
with the DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).

Intro:
What's the hook?
What are the contributions?

Background:
Workflows, etc. - Short, then point to longer discussion in the appendix.
Ontologies - Semantic Web, {RDF,RDFS,OWL}, CWL, ICE data structures

Results:
Strategy - Merge CWL and ICE. Develop - if needed - optimization ontology components
Discuss final product. Point to any additional appendices instead of including in the body.

Case Studies:
Data/Analysis - ICEMAN
M&S - AM?
Optimization - AM or QC?

\input{ack}
\input{appendix}

% The bibliography 
\bibliographystyle{ACM-Reference-Format}
\bibliography{bib}

\end{document}
